Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-12-01 ms.qmd
Notes to prep intro

>>>>

1. Phenotypic plasticity and evolutionary adatation to novel environments
2. Capacity for plasticity and adaptation differ between aqautic and terrestrial ectotherms
3. Climate change is expected to impact on the capacity for plasticity and adaptation
4. We test whether climate variability and predictability explain a populations acclimation capacity and affect changes in trait variance.
